The CrypTool Script: \\ Cryptography, Mathematics and more \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free eLearning program CrypTool\\ (9th edition -- distributed with CrypTool version 1.4.20)} \vspace{60pt}

### 2009-06-30 script/en/chapters/authors.tex
typo
Use the book class for the script, instead of the article class

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\hypertarget{appendix-authors}{}
\subsection{Authors of the CrypTool Script\index{CrypTool}}
\label{s:appendix-authors}

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\newpage
\hypertarget{appendix-movies}{}%neu
\subsection{Bibliography of Movies and Fictional Literature with Relation
to Cryptograpy, Books for Kids with Collections of Simple Ciphers}
\label{s:appendix-movies}
% {\bf movies and literature related to cryptography}(see appendix \ref{s:appendix-movies})
\index{Movies}
\index{Literature}

@@

\subsubsection{For Grownups}

@@

\item[\textrm{[Simmel1970]}] \index{Simmel 1970}
    Johannes Mario Simmel, \\
    {\em And Jimmy went to the Rainbow (original title: Und Jimmy ging zum Regenbogen)}, Knaur Verlag, 1970. \\
    The novel plays between 19938 and 1967 in Vienna. The main character Manual Arandan uncovers step by step the past of his murdered father. Important for the plot is an encrypted manuscript, which is decrypted in chapter 33. In the novel the cipher is called ``25-fold Caesar cipher''. It is actually a Vigen\`ere cipher with a 25 character key.\\
    A movie of the novel appeared in 1971.\\

@@

\vskip +60 pt
\subsubsection{For Kids}

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\newpage
\hypertarget{appendix-Learn-NT}{}
\subsection{Learning Tool for Elementary Number Theory}
    \label{s:appendix-Learn-NT}  
    \index{NT, Learning Tool for Number Theory}%
    \index{Educational tool NT}%

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\clearpage
\listoffigures
\addcontentsline{toc}{section}{\listfigurename}

\clearpage
\listoftables
\addcontentsline{toc}{section}{\listtablename}

>>>>

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\hypertarget{appendix-authors}{}
\section{Authors of the CrypTool Script\index{CrypTool}}
\label{s:appendix-authors}

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\newpage
\hypertarget{appendix-movies}{}%neu
\section{Bibliography of Movies and Fictional Literature with Relation
to Cryptograpy, Books for Kids with Collections of Simple Ciphers}
\label{s:appendix-movies}
% {\bf movies and literature related to cryptography}(see appendix \ref{s:appendix-movies})
\index{Movies}
\index{Literature}

@@

\subsection{For Grownups}

@@

\item[\textrm{[Simmel1970]}] \index{Simmel 1970}
    Johannes Mario Simmel, \\
    {\em And Jimmy went to the Rainbow (original title: Und Jimmy ging zum Regenbogen)}, Knaur Verlag, 1970. \\
    The novel plays between 19938 and 1967 in Vienna. The main character Manual Aranda uncovers step by step the past of his murdered father. Important for the plot is an encrypted manuscript, which is decrypted in chapter 33. In the novel the cipher is called ``25-fold Caesar cipher''. It is actually a Vigen\`ere cipher with a 25 character key.\\
    A movie of the novel appeared in 1971.\\

@@

\vskip +60 pt
\subsection{For Kids}

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\newpage
\hypertarget{appendix-Learn-NT}{}
\section{Learning Tool for Elementary Number Theory}
    \label{s:appendix-Learn-NT}  
    \index{NT, Learning Tool for Number Theory}%
    \index{Educational tool NT}%

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\clearpage
\listoffigures
\addcontentsline{toc}{chapter}{\listfigurename}

\clearpage
\listoftables
\addcontentsline{toc}{chapter}{\listtablename}

### 2009-06-30 script/en/chapters/crypto2020.tex
Use the book class for the script, instead of the article class

\newpage
\hypertarget{Chapter_Crypto2020}{}
\section{Crypto2020 --- Perspectives for long-term cryptographic
         security\index{Security!long-term}}
\label{Chapter_Crypto2020}
\begin{sloppypar}
(Johannes Buchmann, Erik Dahmen, Alexander May and Ulrich Vollmer, TU Darmstadt, May~2007)\\
\end{sloppypar}

\begin{abstract}Ever more powerful hardware and new
  mathematical algorithms threaten to undermine
  the security of cryptographic keys and schemes.
  How long will the methods we use today be able
  to keep what they promise?  And which
  alternatives are on the horizon?
\end{abstract}

@@

\subsection{Widely used schemes}
\label{sec:the-weak}

@@

\subsection{Preparation for tomorrow}
\label{sec:preparations}

@@

\subsection{New mathematical problems}
\label{sec:problems}

@@

\subsection{New signatures}
\label{sec:signatures}

@@

%\subsection{Quantum cryptography -- a loophole?}
\subsection{Quantum cryptography -- a way out of the impasse?}
\label{sec:quantum cryptography}\index{Quantum cryptography}

@@

\subsection{Conclusion}
\label{sec:conclusion}

>>>>

\newpage
\hypertarget{Chapter_Crypto2020}{}
\chapter{Crypto2020 --- Perspectives for long-term cryptographic
         security\index{Security!long-term}}
\label{Chapter_Crypto2020}
\begin{sloppypar}
(Johannes Buchmann, Erik Dahmen, Alexander May and Ulrich Vollmer, TU Darmstadt, May~2007)\\
\end{sloppypar}

% \begin{abstract}Ever more powerful hardware and new
%   mathematical algorithms threaten to undermine
%   the security of cryptographic keys and schemes.
%   How long will the methods we use today be able
%   to keep what they promise?  And which
%   alternatives are on the horizon?
% \end{abstract}

@@

\section{Widely used schemes}
\label{sec:the-weak}

@@

\section{Preparation for tomorrow}
\label{sec:preparations}

@@

\section{New mathematical problems}
\label{sec:problems}

@@

\section{New signatures}
\label{sec:signatures}

@@

%\subsection{Quantum cryptography -- a loophole?}
\section{Quantum cryptography -- a way out of the impasse?}
\label{sec:quantum cryptography}\index{Quantum cryptography}

@@

\section{Conclusion}
\label{sec:conclusion}

### 2009-06-30 script/en/chapters/cryptomethods.tex
Use the book class for the script, instead of the article class

@@

\hypertarget{Kapitel_1}{}
\section{Encryption Procedures}
(Bernhard Esslinger, May 1999; Updates Dec. 2001, Feb. 2003, June 2005, July 2007)

@@

% --------------------------------------------------------------------------
\subsection[Symmetric encryption]
{Symmetric encryption\footnotemark}
  \footnotetext{%
    With CrypTool\index{CrypTool} you can execute the following modern
    symmetric encryption algorithms 
    (using the menu path {\bf Crypt \textbackslash{} Symmetric (modern)}): \\
    IDEA, RC2, RC4, DES (ECB), DES (CBC), Triple-DES (ECB), Triple-DES (CBC),
    MARS (AES candidate), RC6 (AES candidate), Serpent (AES candidate), 
    Twofish (AES candidate), Rijndael (official AES algorithm).
  }

@@

% --------------------------------------------------------------------------
\subsubsection{New results about cryptanalysis of AES}
\index{Cryptanalysis} \label{NeueAES-Analyse}

@@

% --------------------------------------------------------------------------
\subsubsection{Current status of brute-force attacks on 
symmetric algorithms (RC5)}
\index{Attack!brute-force}
\index{RC5}
\label{Brute-force-gegen-Symmetr}

@@

% --------------------------------------------------------------------------
\subsection[Asymmetric encryption]
{Asymmetric encryption\footnotemark}
  \footnotetext{%
    With CrypTool\index{CrypTool} you can execute RSA encryption
    and decryption (using the menu path {\bf Crypt \textbackslash{} Asymmetric}).
    In both cases you must select a RSA key pair. Only in the case of decryption
    the secret RSA key is necessary: so here you are asked to enter the PIN. 
  }

@@

% --------------------------------------------------------------------------
% \newpage
\subsection[Hybrid procedures]
{Hybrid procedures\footnotemark}
\footnotetext{%
Within CrypTool\index{CrypTool} you can find this technique using the menu
path {\bf Crypt \textbackslash{} Hybrid}: 
There you can follow the single steps and its dependencies with concrete
numbers. The variant with RSA as the asymmetric algorithm is graphically
visualized; the variant with ECC uses the standard dialogs. In both cases
AES is used as the symmetric algorithm.
}\index{Hybrid procedure}

@@

% --------------------------------------------------------------------------
\subsection{Further details}

@@

% --------------------------------------------------------------------------
\newpage
\begin{thebibliography}{99999}
\addcontentsline{toc}{subsection}{Bibliography}

@@

% --------------------------------------------------------------------------
\newpage
\section*{Web links}\addcontentsline{toc}{subsection}{Web links}

>>>>

\hypertarget{Kapitel_1}{}
\chapter{Encryption Procedures}
(Bernhard Esslinger, May 1999; Updates Dec. 2001, Feb. 2003, June 2005, July 2007)

@@

@@

% --------------------------------------------------------------------------
\section[Symmetric encryption]
{Symmetric encryption\footnotemark}
  \footnotetext{%
    With CrypTool\index{CrypTool} you can execute the following modern
    symmetric encryption algorithms 
    (using the menu path {\bf Crypt \textbackslash{} Symmetric (modern)}): \\
    IDEA, RC2, RC4, DES (ECB), DES (CBC), Triple-DES (ECB), Triple-DES (CBC),
    MARS (AES candidate), RC6 (AES candidate), Serpent (AES candidate), 
    Twofish (AES candidate), Rijndael (official AES algorithm).
  }

@@

% --------------------------------------------------------------------------
\subsection{New results about cryptanalysis of AES}
\index{Cryptanalysis} \label{NeueAES-Analyse}

@@

% --------------------------------------------------------------------------
\subsection{Current status of brute-force attacks on
symmetric algorithms (RC5)}
\index{Attack!brute-force}
\index{RC5}
\label{Brute-force-gegen-Symmetr}

@@

% --------------------------------------------------------------------------
\section[Asymmetric encryption]
{Asymmetric encryption\footnotemark}
  \footnotetext{%
    With CrypTool\index{CrypTool} you can execute RSA encryption
    and decryption (using the menu path {\bf Crypt \textbackslash{} Asymmetric}).
    In both cases you must select a RSA key pair. Only in the case of decryption
    the secret RSA key is necessary: so here you are asked to enter the PIN. 
  }

@@

% --------------------------------------------------------------------------
% \newpage
\section[Hybrid procedures]
{Hybrid procedures\footnotemark}
\footnotetext{%
Within CrypTool\index{CrypTool} you can find this technique using the menu
path {\bf Crypt \textbackslash{} Hybrid}: 
There you can follow the single steps and its dependencies with concrete
numbers. The variant with RSA as the asymmetric algorithm is graphically
visualized; the variant with ECC uses the standard dialogs. In both cases
AES is used as the symmetric algorithm.
}\index{Hybrid procedure}

@@

% --------------------------------------------------------------------------
\section{Further details}

@@

% --------------------------------------------------------------------------
\newpage
\begin{thebibliography}{99999}
\addcontentsline{toc}{section}{Bibliography}

@@

% --------------------------------------------------------------------------
\newpage
\section*{Web links}
\addcontentsline{toc}{section}{Web links}

### 2009-06-30 script/en/chapters/digitalsignatures.tex
Use the book class for the script, instead of the article class

\newpage
% --------------------------------------------------------------------------
\hypertarget{Chapter_Hashes-and-Digital-Signatures}{}
\section{Hash Functions and Digital Signatures}
\label{Chapter_Hashes-and-Digital-Signatures}
\index{Signature!digital}
(Schneider J. / Esslinger B. / Koy H., June 2002;
Updates: Feb. 2003, June 2005)

@@

% --------------------------------------------------------------------------
\hypertarget{Hash-functions-ht}{}
\subsection{Hash functions}
\index{Hash function}
A {\em hash function}\footnote{%
Hash algorithms compute a condensed representation of electronic data
(message).
When a message is input to a hash algorithm, the result is an output called
a message digest. The message digests typically range in length 
from 128 to 512 bits, depending on the algorithm. 
Secure hash algorithms are typically used with
other cryptographic algorithms, such as digital signature algorithms and
keyed-hash message authentication codes, or in the generation of random
numbers (bits).
}
maps a message of any length to a string of characters with a constant size,
the \index{Hash value} hash value.

% --------------------------------------------------------------------------
\vskip + 15pt
\subsubsection{Requirements for hash functions}

@@

% --------------------------------------------------------------------------
\vskip + 15pt
\subsubsection{Current attacks against hash functions like SHA-1}
\label{collision-attacks-against-sha-1}

@@

% --------------------------------------------------------------------------
\vskip + 15pt
\subsubsection{Signing with hash functions}
The signature procedure with hash functions is as follows:\footnote{% 
Compare: \href{http://en.wikipedia.org/wiki/Digital\_signature}
      {\texttt{http://en.wikipedia.org/wiki/Digital\_signature}}.
} \\ Rather than signing the actual
document, the sender now first calculates the hash value of the message and
signs this. The recipient also calculates the hash value of the message (the
algorithm used must be known), then verifies whether the signature sent with the
message is a correct signature of the hash value. If this is the case, the
signature is verified to be correct. This means that the message is authentic,
because we have assumed that knowledge of the public key does not enable you to
derive the secret key. However, you would need this secret key to sign messages
in another name.

@@

% --------------------------------------------------------------------------
\vskip + 15pt
\subsection{RSA signatures}
\index{Signature!digital}
\index{RSA!signature}

@@

% --------------------------------------------------------------------------
\vskip + 15pt
\subsection{DSA signatures}
\index{Signature!digital}
\index{DSA!signature}

@@

% --------------------------------------------------------------------------
\vskip + 15pt
\subsection{Public key certification}
\index{Certification!public key}
\index{PKI}
The aim of public key certification is to guarantee the connection between a
public key and a user and to make it traceable for external parties. In cases in
which it is impossible to ensure that a public key really belongs to a
particular person, many protocols are no longer secure, even if the individual
cryptographic modules cannot be broken.

% --------------------------------------------------------------------------
\vskip + 15pt
\subsubsection{Impersonation attacks}\label{Impersonalisierungsattacke}
\index{Impersonation attack}
Assume Charlie has two pairs of keys (PK1, SK1) and (PK2, SK2), where SK denotes
the secret key and PK the public key. Further assume that he manages to palm off
PK1 on Alice as Bob's public key and PK2 on Bob as Alice's public key (by
falsifying a public key directory).

@@

% --------------------------------------------------------------------------
\vskip + 15pt
\subsubsection{X.509 certificate}
\index{X.509} 
Each participant who wants to have an X.509 certificate (\cite{X.509})
verifying that his public key belongs to a real person consults what is
known as a \index{Certification authority (CA)} certification authority
(CA)\footnote{%
Often called trust center, if the certificates are not only offered
to a closed user group.
}. 
He proves his identity to this CA (for example by showing his ID). 
The CA then issues him an electronic document (certificate) which 
essentially contains the name of the certificate-holder and the name
of the CA, the certificate-holder's public key and the validity period
of the certificate. The CA then signs the certificate using its secret key.

@@

\newpage
\begin{thebibliography}{99999}
\addcontentsline{toc}{subsection}{Bibliography}

>>>>

\newpage
% --------------------------------------------------------------------------
\hypertarget{Chapter_Hashes-and-Digital-Signatures}{}
\chapter{Hash Functions and Digital Signatures}
\label{Chapter_Hashes-and-Digital-Signatures}
\index{Signature!digital}
(Schneider J. / Esslinger B. / Koy H., June 2002;
Updates: Feb. 2003, June 2005)

@@

% --------------------------------------------------------------------------
\hypertarget{Hash-functions-ht}{}
\section{Hash functions}
\index{Hash function}
A {\em hash function}\footnote{%
Hash algorithms compute a condensed representation of electronic data
(message).
When a message is input to a hash algorithm, the result is an output called
a message digest. The message digests typically range in length 
from 128 to 512 bits, depending on the algorithm. 
Secure hash algorithms are typically used with
other cryptographic algorithms, such as digital signature algorithms and
keyed-hash message authentication codes, or in the generation of random
numbers (bits).
}
maps a message of any length to a string of characters with a constant size,
the \index{Hash value} hash value.

% --------------------------------------------------------------------------
\vskip + 15pt
\subsection{Requirements for hash functions}

@@

% --------------------------------------------------------------------------
\vskip + 15pt
\subsection{Current attacks against hash functions like SHA-1}
\label{collision-attacks-against-sha-1}

@@

% --------------------------------------------------------------------------
\vskip + 15pt
\subsection{Signing with hash functions}
The signature procedure with hash functions is as follows:\footnote{% 
Compare: \href{http://en.wikipedia.org/wiki/Digital\_signature}
      {\texttt{http://en.wikipedia.org/wiki/Digital\_signature}}.
} \\ Rather than signing the actual
document, the sender now first calculates the hash value of the message and
signs this. The recipient also calculates the hash value of the message (the
algorithm used must be known), then verifies whether the signature sent with the
message is a correct signature of the hash value. If this is the case, the
signature is verified to be correct. This means that the message is authentic,
because we have assumed that knowledge of the public key does not enable you to
derive the secret key. However, you would need this secret key to sign messages
in another name.

@@

% --------------------------------------------------------------------------
\vskip + 15pt
\section{RSA signatures}
\index{Signature!digital}
\index{RSA!signature}

@@

% --------------------------------------------------------------------------
\vskip + 15pt
\section{DSA signatures}
\index{Signature!digital}
\index{DSA!signature}

@@

% --------------------------------------------------------------------------
\vskip + 15pt
\section{Public key certification}
\index{Certification!public key}
\index{PKI}
The aim of public key certification is to guarantee the connection between a
public key and a user and to make it traceable for external parties. In cases in
which it is impossible to ensure that a public key really belongs to a
particular person, many protocols are no longer secure, even if the individual
cryptographic modules cannot be broken.

% --------------------------------------------------------------------------
\vskip + 15pt
\subsection{Impersonation attacks}\label{Impersonalisierungsattacke}
\index{Impersonation attack}
Assume Charlie has two pairs of keys (PK1, SK1) and (PK2, SK2), where SK denotes
the secret key and PK the public key. Further assume that he manages to palm off
PK1 on Alice as Bob's public key and PK2 on Bob as Alice's public key (by
falsifying a public key directory).

@@

% --------------------------------------------------------------------------
\vskip + 15pt
\subsection{X.509 certificate}
\index{X.509} 
Each participant who wants to have an X.509 certificate (\cite{X.509})
verifying that his public key belongs to a real person consults what is
known as a \index{Certification authority (CA)} certification authority
(CA)\footnote{%
Often called trust center, if the certificates are not only offered
to a closed user group.
}. 
He proves his identity to this CA (for example by showing his ID). 
The CA then issues him an electronic document (certificate) which 
essentially contains the name of the certificate-holder and the name
of the CA, the certificate-holder's public key and the validity period
of the certificate. The CA then signs the certificate using its secret key.

@@

\newpage
\begin{thebibliography}{99999}
\addcontentsline{toc}{section}{Bibliography}

### 2009-06-30 script/en/chapters/ellipticcurves.tex
1.4.20 updates
Use the book class for the script, instead of the article class

\newpage
\hypertarget{ellcurve}{}
\section{Elliptic Curves}
\label{Chapter_EllipticCurves}
\index{Elliptic curves}
(Filipovics B. / B\"uger M. / Esslinger B. / Oyono R., April 2000, Updates: Dec. 2001, June 2002, Mar. 2003)

\subsection{Elliptic curve cryptography -- a high-performance substitute for RSA?}
\index{Performance}
\label{ECAlternative}

@@

\subsection{Elliptic curves -- history}

@@

\subsection{Elliptic curves -- mathematical basics}

@@

\subsubsection{Groups}

@@

\subsubsection{Fields}

@@

% -----------------------------------------------------------------------------
\subsection{Elliptic curves in cryptography}\label{ECC-Crypto}

@@

% -----------------------------------------------------------------------------
\subsection{Operating on the elliptic curve}

@@

% \newpage
\begin{figure}[htbp]
\subsubsection*{How to add points on an elliptic curve}
The following figures show how points on an elliptic curve over the field of real numbers are summed up using affine coordinates.
We note that the point infinity ${\cal O}$ cannot be shown in the affine plane.  
\begin{center}
\includegraphics[scale=1.08]{figures/ec-mult2}
\caption{Doubling of a point} 
\vspace{\floatsep}
\vskip +20 pt
\includegraphics[scale=0.65]{figures/ec-add}
\caption{Summing up two different points over the real number field} % \footnotemark }
\end{center}
\end{figure}
\enlargethispage{+20pt}
\newpage

% -----------------------------------------------------------------------------
\subsection{Security of elliptic-curve-cryptography: The ECDLP}

@@

% -----------------------------------------------------------------------------
\subsection{Encryption and signing with elliptic curves}

@@

\par
%\smallskip
%{\bf Encryption:}
\subsubsection{Encryption}

@@

\par
%\smallskip 
%{\bf Signing:}
\subsubsection{Signing}

@@

\par
%\smallskip 
%{\bf Signature Verification:}
\subsubsection{Signature verification}

@@

% -----------------------------------------------------------------------------
\hypertarget{faktell}{}
\subsection{Factorisation using elliptic curves} \label{ECC-Factorisation}

@@

% -----------------------------------------------------------------------------
\subsection{Implementing elliptic curves}

@@

% -----------------------------------------------------------------------------
\subsection{Elliptic curves in use}

@@

In Austria has been massively launched: A bank card with digital signature function.

@@

%--------------------------------------------------------------------
\newpage
%\addcontentsline{toc}{subsection}{Literaturverzeichnis}
\begin{thebibliography}{99999}
\addcontentsline{toc}{subsection}{Bibliography}

@@

%--------------------------------------------------------------------
%\newpage
\section*{Web links}\addcontentsline{toc}{subsection}{Web links}

>>>>

\newpage
\hypertarget{ellcurve}{}
\chapter{Elliptic Curves}
\label{Chapter_EllipticCurves}
\index{Elliptic curves}
(Filipovics B. / B\"uger M. / Esslinger B. / Oyono R., April 2000, Updates: Dec. 2001, June 2002, Mar. 2003)

\section{Elliptic curve cryptography -- a high-performance substitute for RSA?}
\index{Performance}
\label{ECAlternative}

@@

\section{Elliptic curves -- history}

@@

\section{Elliptic curves -- mathematical basics}

@@

\subsection{Groups}

@@

\subsection{Fields}

@@

% -----------------------------------------------------------------------------
\section{Elliptic curves in cryptography}\label{ECC-Crypto}

@@

% -----------------------------------------------------------------------------
\section{Operating on the elliptic curve}

@@

% \newpage
\begin{figure}[htbp]
\subsection*{How to add points on an elliptic curve}
The following figures show how points on an elliptic curve over the field of real numbers are summed up using affine coordinates.
We note that the point infinity ${\cal O}$ cannot be shown in the affine plane.  
\begin{center}
\includegraphics[scale=1.08]{figures/ec-mult2}
\caption{Doubling of a point} 
\vspace{\floatsep}
\vskip +20 pt
\includegraphics[scale=0.65]{figures/ec-add}
\caption{Summing up two different points over the real number field} % \footnotemark }
\end{center}
\end{figure}
\enlargethispage{+20pt}
\newpage

% -----------------------------------------------------------------------------
\section{Security of elliptic-curve-cryptography: The ECDLP}

@@

% -----------------------------------------------------------------------------
\section{Encryption and signing with elliptic curves}

@@

\par
%\smallskip
%{\bf Encryption:}
\subsection{Encryption}

@@

\par
%\smallskip 
%{\bf Signing:}
\subsection{Signing}

@@

\par
%\smallskip 
%{\bf Signature Verification:}
\subsection{Signature verification}

@@

% -----------------------------------------------------------------------------
\hypertarget{faktell}{}
\section{Factorisation using elliptic curves} \label{ECC-Factorisation}

@@

% -----------------------------------------------------------------------------
\section{Implementing elliptic curves}

@@

% -----------------------------------------------------------------------------
\section{Elliptic curves in use}

@@

In Austria ECC has been massively launched: A bank card with digital signature function.

@@

%--------------------------------------------------------------------
\newpage
%\addcontentsline{toc}{subsection}{Literaturverzeichnis}
\begin{thebibliography}{99999}
\addcontentsline{toc}{section}{Bibliography}

@@

%--------------------------------------------------------------------
%\newpage
\section*{Web links}
\addcontentsline{toc}{section}{Web links}

### 2009-06-30 script/en/chapters/introduction.tex
Use the book class for the script, instead of the article class

% --------------------------------------------------------------------------
\section*{Preface to the 8th Edition of the CrypTool Script\footnote{For the 9th edition no extra preface was written.}}
\addcontentsline{toc}{section}{Preface to the 8th Edition of the CrypTool Script}

@@

% --------------------------------------------------------------------------
\newpage
\section*{Introduction -- How do the Script and the Program Play together?}  \addcontentsline{toc}{section}{Introduction -- How do the Script and the Program Play together?}

>>>>

% --------------------------------------------------------------------------
\chapter*{Preface to the 8th Edition of the CrypTool Script\footnote{For the 9th edition no extra preface was written.}}
\addcontentsline{toc}{chapter}{Preface to the 8th Edition of the CrypTool Script}

@@

% --------------------------------------------------------------------------
\newpage
\chapter*{Introduction -- How do the Script and the Program Play together?}
\addcontentsline{toc}{chapter}{Introduction -- How do the Script and the Program Play together?}
